ROV report

### 2020-03-23 analysis/reports/rov.Rmd
plots

@@

@@

@@

>>>>

all_di_singletons <- filter(all_di, s0 > 2, dat != "portal_plants", singletons)

rov_long_singletons <- all_di_singletons %>%
  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts, thresholded_nparts) %>%
  tidyr::pivot_longer(cols = starts_with("mean"),
                      names_to = "rov_index",
                      values_to = "val")

@@

rov_long_singletons <- rov_long_singletons %>%
  group_by(rov_index) %>%
  mutate(binned_val = bin_rov(val, nbins =5 ),
         qbinned_val = bin_rov(val, nbins = 5, quantiles = T),
         qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T)) %>%
  ungroup()

all_di_singletons <- all_di_singletons %>%
  mutate(qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T))

@@

```{r qbinned nparts ROV high n}

@@

### Rarefaction
```{r rarefaction percentiles overall}

ggplot(all_di_singletons, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()

ggplot(all_di_singletons, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()
```

```{r rarefaction percentiles binned by nparts}

ggplot(all_di_singletons, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)

ggplot(all_di_singletons, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)

```{r rarefaction change}

all_di_change <- select(all_di, dat, site, singletons, s0, n0, log_nparts, qbinned_lognparts, skew_percentile, simpson_percentile) %>%
  bind_rows(select(all_di_singletons, dat, site, singletons, s0, n0, skew_percentile, simpson_percentile)) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(s0, n0, skew_percentile, simpson_percentile, log_nparts, qbinned_lognparts)) %>%
  select(-log_nparts_TRUE, -qbinned_lognparts_TRUE) %>%
  filter(!is.na(s0_FALSE)) %>%
  mutate(s0_change = s0_TRUE - s0_FALSE,
         n0_change = n0_TRUE - n0_FALSE,
         skew_change = skew_percentile_TRUE - skew_percentile_FALSE,
         even_change = simpson_percentile_TRUE - simpson_percentile_FALSE)

ggplot(all_di_change, aes(skew_percentile_FALSE, skew_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0, 100) +
  geom_abline(intercept = 0, slope = 1, color = "orange")

ggplot(all_di_change, aes(log(s0_FALSE), log(n0_FALSE), color = skew_percentile_TRUE < skew_percentile_FALSE)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d(begin = .1, end = .9) +
  theme(legend.position = "top")

ggplot(all_di_change, aes(skew_percentile_FALSE, skew_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  facet_wrap(vars(qbinned_lognparts_FALSE), nrow = 2) +
  xlim(0, 100) +
  ylim(0, 100) +
  geom_abline(intercept = 0, slope = 1, color = "orange")

ggplot(all_di_change, aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0, 100) +
  geom_abline(intercept = 0, slope = 1, color = "orange")
ggplot(all_di_change, aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  facet_wrap(vars(qbinned_lognparts_FALSE), nrow = 2) +
  xlim(0, 100) +
  ylim(0, 100) +
  geom_abline(intercept = 0, slope = 1, color = "orange")
```
